\documentclass[psamsfonts]{amsart}

%-------Packages---------
\usepackage{amssymb,amsfonts,amsthm}
\usepackage[all,arc]{xy}
\usepackage{enumerate}
\usepackage{mathrsfs}
\usepackage[pdftex]{graphicx}

%--------Theorem Environments--------
%theoremstyle{plain} --- default
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{quest}[thm]{Question}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{defns}[thm]{Definitions}
\newtheorem{con}[thm]{Construction}
\newtheorem{exmp}[thm]{Example}
\newtheorem{exmps}[thm]{Examples}
\newtheorem{notn}[thm]{Notation}
\newtheorem{notns}[thm]{Notations}
\newtheorem{addm}[thm]{Addendum}
\newtheorem{exer}[thm]{Exercise}

\theoremstyle{remark}
\newtheorem{rem}[thm]{Remark}
\newtheorem{rems}[thm]{Remarks}
\newtheorem{warn}[thm]{Warning}
\newtheorem{sch}[thm]{Scholium}

\makeatletter
\let\c@equation\c@thm
\makeatother
\numberwithin{equation}{section}

\bibliographystyle{plain}

%--------Meta Data: Fill in your info------
\title{Mean connectome}

\author{Erika Dunn-Weiss}

\date{Mar 2, 2015}

\begin{document}
\maketitle

\section{Posed Statistical Decision Theoretic}
This is an attempt to follow my notes from class and replicate what we discussed. 

\subsection{Sample Space}
$\Omega = \mathcal{A}_n = \{0,1\}^{n\times n}$, the set of adjacency matrices $\mathcal{A}_n$ on graphs $\mathcal{G}_n = (V,E,Y)$.

\subsection{Model}
$P = SBM^k_n(\rho, \beta)$. We posit the probability of an edge between $u,v$ is given by $P(u \sim v) = P_{uv}$ and the distribution of edges between any pair of vertices $u,v$ is $a_{u,v} \sim Bern(P_{uv})$

\subsection{Action Space}
$A = (0,1)^n \subseteq \Theta$, where $\Theta$ is the parameter space. This is desirable since this is a parameter estimation problem. 

\subsection{Decision Rule Class} 
The decision rule is to minimize the loss defined by the loss function below. 

\subsection{Loss Function}
$l : \Theta \times A \to \mathbb R_{> 0} $ where $l(\theta,\delta(\Omega))$ is the cost of action $\delta$ under parameter $\theta$. More explicitly, $l(\theta, \delta(\Omega)) = \prod_{u v} \hat{P_{uv}} ^{a_{uv}} (1 - \hat{P_{uv}}^{1 - a_{uv}})$, where $\hat{P_{uv}} = \frac{1}{m} \sum^m a_{uv} + \frac{\epsilon}{m^2}$ such that $\frac{\epsilon}{m^2} \leftarrow 0$ asymptotically. Since $P_{uv}\in [0,1]$, you have issues at the boundaries when $P_{u v} $ = 0 or 1, as the whole estimation becomes zero probability. Thus the use of $\hat{P}$ is a necessary smoothing. 

\subsection{Risk Function}
$R(\theta, \delta) = E_{p}(L(\theta,\delta(\Omega)))$. The risk function is taken as the expected loss.



 
 \end{document}